{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-05 Notebook LaTEX/Proposal/main.tex
>w<, changes

            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert^2$. 

@@

        \todoinline{Add more details about what they actually did in the original paper. }

@@

        He also provided rigorous convergence claim under various scenarios of inner loop termination strategies. 

@@

        The paper is phenomenal at addressing the following: 

@@

            \item Getting the error sequence $(\epsilon_k)_{k \ge 0}$ to asserts fast convergence of the outer loop. 
            \item Two termination criteria for the inner loop given the desired accuracy which expedite the convergence and makes simpler proofs for the convergence of the overall algorithm. 

@@

    \subsection{Consequences of the inner loop termination criteria}
        Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which of practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator. 
        For theoretical interests, the absolute and relative criteria C1, C2 places bound on the true error of the gradient of Moreau Envelope at the point $x$. 
        \par 
        The following are results proved in Lin's second Catalyst paper. 
        Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the approximated gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
        Then
        \begin{align*}
            \left\Vert z - \mathcal J_{\kappa^{-1}F} (x)\right\Vert
            &\le \sqrt{\frac{2\epsilon}{\kappa}} 
            \iff 
            \left\Vert
                \mathcal G_{\kappa^{-1}F}^\epsilon(z) 
                - \nabla \mathcal M_{F, \kappa^{-1}}^*(x)
            \right\Vert 
            \le \sqrt{2\kappa\epsilon}. 
        \end{align*}
        Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have: 
        \begin{align*}
            \Vert z - \mathcal J_{\kappa^{-1}F}(x)\Vert 
            &\le \sqrt{\delta}\Vert x - z\Vert 
            \le \sqrt{\delta}(
                \Vert x - \mathcal J_{\kappa^{-1}F} (x) \Vert 
                - \Vert z - \mathcal J_{\kappa^{-1}F} (x) \Vert
            ), 
            \\
            \left\Vert 
                \widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) - 
                \nabla \mathcal M^*_{F, \kappa^{-1}}(x) 
            \right\Vert
            &\le 
            \delta' \Vert \nabla \mathcal M^*_{F, \kappa^{-1}}(x) \Vert \quad 
            \text{with } \delta' = \sqrt{\delta}/(1 - \sqrt{\delta}). 
        \end{align*}
        \par 
        For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see 
        \todo{
            $\square$ Add paper: ``First-order methods of smooth convex optimization with inexact oracle'' \\
            $\square$ Cite them. 
        }
        {\hl{Devolder et al.}}
        \par
        Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$, we can also terminate $\mathbb M$ after a fixed number of iteration. 
        This is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
        It needs a precise bound on the complexity for $\mathbb M$ to achieve C1, or C2 of the strongly convex function $\mathcal M^{\kappa^{-1}}_F(\cdot; y)$. 
        \par
        To attain an optimal convergence rate for $\mathbb A$ on criterion C1, the error sequence $(\epsilon_k)_{k \ge 0}$ should be given by Equation \ref{eqn:catalyst-error-seq-cnvx} for convex $F$, and \ref{eqn:catalyst-error-seq-s-cnvx} for strongly convex $F$. 
        Amazingly, termination criterion C2 doesn't require knowledge on $F^*$ to achieve optimal convergence for $\mathbb A$. 
        The following schedules for $(\delta_k)_{k \ge 0}$ are given in Lin, et al.'s second Catalyst paper, the error sequence $\delta_k$ for criterion C2 is given by: 
        \begin{align*}\label{eqn:catalyst-rel-error-seq}
            q &= \mu/(\mu + \kappa), 
            \\
            \delta_k 
            &= \frac{\sqrt{q}}{2 - \sqrt{q}} \text{ if } \mu > 0, 
            \\
            \delta_k &= \frac{1}{(k + 1)^2} \text{ if }\mu = 0. 
        \end{align*}
        Let's pay particular attention to criterion C2.

>>>>

            \item $L, \mu$, the Lipschitz constant and the strong convexity constant for the smooth part of the objective are not known prior, and it's estimated through $A$ by $\mu = 1/\Vert (A^TA)^{-1}\Vert$ and $L = \Vert A^TA\Vert$. 

@@

@@

            Add more details about what they actually did in the original paper.
                \item [$\square$] The condition of warm starting in the algorithm and complexity bound of the inner loop. 

@@

        The paper has the following new ideas: 

@@

            \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in a error sequence without $F^*$, and simplier proof without using the Nesterov's estimating sequence. 
            \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth compositie objective. 

@@

    \subsection{Consequences of the inner loop termination criteria}
        Lemma \ref{lemma:sufficient-c1} describes a sufficient conditions to verify the membership of $\bar z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$ through the proximal gradient operator on $F:= f_\kappa(z) + g(z)$ which of practical importance because it translates criterion C1 into something implementable, i.e: the proximal gradient operator. 
        For theoretical interests, the absolute and relative criteria C1, C2 places bound on the true error of the gradient of Moreau Envelope at the point $x$. 
        The following are results proved in Lin's second Catalyst paper. 
        Given any $\epsilon > 0$ if $z \in \mathcal J_{\kappa^{-1}F}^\epsilon (x)$, define the approximated gradient mapping $\mathcal G_{\kappa^{-1}F}^\epsilon (z) := \kappa(x - z)$.
        Then
            \left\Vert z - \mathcal J_{\kappa^{-1}F} (x)\right\Vert
            &\le \sqrt{\frac{2\epsilon}{\kappa}} 
            \left\Vert
                \mathcal G_{\kappa^{-1}F}^\epsilon(z) 
                - \nabla \mathcal M_{F, \kappa^{-1}}^*(x)
            \right\Vert 
            \le \sqrt{2\kappa\epsilon}. 
        Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have: 
            \Vert z - \mathcal J_{\kappa^{-1}F}(x)\Vert 
            &\le \sqrt{\delta}\Vert x - z\Vert 
            \le \sqrt{\delta}(
                \Vert x - \mathcal J_{\kappa^{-1}F} (x) \Vert 
                - \Vert z - \mathcal J_{\kappa^{-1}F} (x) \Vert
            ), 
            \left\Vert 
                \widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) - 
                \nabla \mathcal M^*_{F, \kappa^{-1}}(x) 
            \right\Vert
            \delta' \Vert \nabla \mathcal M^*_{F, \kappa^{-1}}(x) \Vert \quad 
            \text{with } \delta' = \sqrt{\delta}/(1 - \sqrt{\delta}). 
        For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see 
            $\square$ Add paper: ``First-order methods of smooth convex optimization with inexact oracle'' \\
        {\hl{Devolder et al.}}
        Their works were earlier and a Nesterov accelerated algorithm using estimating sequence and inexact oracles was derived. 
        Finally, besides C1, C2 criteria which, the ``Fixed Budget" termination criterion assesses the optimality of results produced by $\mathbb M$, we can also terminate $\mathbb M$ after a fixed number of iteration. 
        This is the original strategy proposed by Lin et al. in their first Catalyst paper in 2015 \cite{lin_universal_2015}. 
        It needs a precise bound on the complexity for $\mathbb M$ to achieve C1, or C2 of the strongly convex function $\mathcal M^{\kappa^{-1}}_F(\cdot; y)$. 
        To attain an optimal convergence rate for $\mathbb A$ on criterion C1, the error sequence $(\epsilon_k)_{k \ge 0}$ should be given by Equation \ref{eqn:catalyst-error-seq-cnvx} for convex $F$, and \ref{eqn:catalyst-error-seq-s-cnvx} for strongly convex $F$. 
        Amazingly, termination criterion C2 doesn't require knowledge on $F^*$ to achieve optimal convergence for $\mathbb A$. 
        The following schedules for $(\delta_k)_{k \ge 0}$ are given in Lin, et al.'s second Catalyst paper, the error sequence $\delta_k$ for criterion C2 is given by: 
        \begin{align*}\label{eqn:catalyst-rel-error-seq}
            q &= \mu/(\mu + \kappa), 
            \delta_k 
            &= \frac{\sqrt{q}}{2 - \sqrt{q}} \text{ if } \mu > 0, 
            \delta_k &= \frac{1}{(k + 1)^2} \text{ if }\mu = 0. 
        Let's pay particular attention to criterion C2.
